Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-13 main.tex
improvements

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

\usepackage{hyperref}         % For hypertext links

@@

% DONE : MV : remove 'For example' 
We illustrate the subject of our discussion with the curl operator. 
% One example application concerns the curl operator. 
If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$. Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{2}(\Omega)}
    .
\end{align*}
The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. 
Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.

@@

When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
as mappings between Lebesgue spaces. 
We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation},
but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
\\
% DONE: cite Guzman and Salgado in a reasonable manner

@@

However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. % DONE: Theo : But -> However 
We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
In comparison to their exposition, our variants of the regularized potential operators are simplified:
we only study them over convex domains and use simpler (that is, constant) weight functions. 
The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
We consider the latter outcome to be of independent interest. 
\todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.

@@

% Future work % DONE: Theo : parts already mentioned ??? 
% Computable reliable estimates are important: 
% they quantify the fundamental stability properties of partial differential equations in vector analysis,
% such as the Hodge Laplace equation. 
Any upper bounds for the Poincar\'e--Friedrichs constant corresponds to a lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
In numerical methods, upper bounds for the Poincar\'e--Friedrichs for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
and they lead to lower bounds for the spectrum of finite element matrices. 
There are several avenues for further research going from here.

The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches. There are at least two points where the present techniques can be improved further. First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star. In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping. 
Better transformations or more careful estimates are likely possible, as are completely different approaches.  For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.

@@

This section is devoted to crucially important geometric constructions. 
Suppose that we have a shellable simplicial complex. 
Every time we add a simplex according to the shelling sequence, 
we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
We will need a homeomorphism from the new simplex on its complement in the newly completed star.
This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
We are particularly interested in the norms of its Jacobian.

This reflection will be used subsequently to generalize the discussion in Section~\ref{section:gradient}
to the setting of differential forms. 
In addition to that, this endeavor will also produce another geometric tool 
which enables an additional possibility to estimate Poincar\'e--Friedrichs constants:
we construct a deformation which maps the entire star into the complement of the newly completed star. 
Again, we give explicit estimates of the Jacobian.

We begin with a geometric observation. 
Suppose that $T$ is any $n$-dimensional simplex with some proper subsimplex $F$.
We want to find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is on only one side of the hyperplane.

\begin{lemma}\label{lemma:oppositesubsimplex}
    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
    Let $F, F'$ be the two subsimplices of $T$ with respective sets of vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
    Then $T$ lies on one side of the affine subspace
    \begin{gather*}
        A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
    \end{gather*}
    Moreover, $F = T \cap A$.
\end{lemma}
\begin{proof}
    Evidently, $A$ has dimension $n-1$ and $F \cap A \cap T$.
    Let us now suppose that $x \in A \cap T$.
    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
    \begin{align*}
        x &= 
        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
        \\&
        = 
        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
        + 
        \sum_{i=1  }^{k  } \lambda_{i} v_i 
        + 
        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
        + 
        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
        .
    \end{align*}
    We know $x$ can be written as a unique convex combination of the vertices of $T$.
    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive. 
    If $x \notin F$, then at least one of these coefficients must be negative. 
    But then their sum must be negative, which is a contradiction. 
    The desired statement follows.         
\end{proof}

@@

\begin{lemma}\label{lemma:stardivision}
    Let $\calT$ be an $n$-dimensional simplicial complex
    such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
    Let $z_S$ be the barycenter of $S$ 
    and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
    If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
    then $\vol(T^{\star}) = \vol(T) / n$.
\end{lemma}
\begin{proof}
    This is easy.
\end{proof}

The main result of this section constructs the desired homeomorphism. 
It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
The construction is completed in several steps,
and the Lipschitz estimate reflects the shape regularity.

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
    Let $S \in \calT$ be a simplex of dimension $k < n$,
    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
    and let 
    \begin{align*}
        U := \overline{ |\patch_{\calT}(S)| \setminus T },
        \qquad 
        {\Gamma_I} := U \cap T,
        \qquad 
        {\Gamma_J} := \overline{ \partial T \setminus \partial U }.
    \end{align*}
    \begin{enumerate}
    \item 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi_{1} : T \rightarrow U
    \end{align*}
    which is the identity along ${\Gamma_I} = T \cap U$ and which satisfies the upper bounds 
    \begin{gather*}
        \| \Jacobian\Xi_{1} \|          \leq \Cfive{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi_{1}^{-1} \|     \leq \Csechs{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi_{1} \|      \leq \Cdetfive{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi_{1}^{-1} \| \leq \Cdetsechs{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
    \item 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi_{2} : T \rightarrow U
    \end{align*}
    which is the identity along $\partial U \setminus \partial T$ and which satisfies the upper bounds 
    \begin{gather*}
        \| \Jacobian\Xi_{2} \|          \leq \Csieb{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi_{2}^{-1} \|     \leq \Cacht{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi_{2} \|      \leq \Cdetsieb{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi_{2}^{-1} \| \leq \Cdetacht{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
    \end{enumerate}
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let ${\Gamma_J} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So ${\Gamma_J}$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that ${\Gamma_J}$ is the union of exactly those faces of $T$ that contain $S'$,
        whereas ${\Gamma_I} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.

@@

        \item 
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ as follows.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}
        By construction, the mapping preserves volumes:
        \begin{align*}
            |\det( \Jacobian      \Theta_{|K} )|
            = 
            |\det( \Jacobian^{-1} \Theta_{|K} )|
            =
            1
            .
        \end{align*}
        We want to characterize the singular values of this transform. 
        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
        We can write
        \begin{align*}
            \Theta_{|K}(x) 
            = 
            x
            - 
            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
            .
        \end{align*}
        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_z$,
        and that it equals $-z_{S'}$ when $x = z_{S'}$.
%         and when $x = z_{S'}$, then 
%         \begin{align*}
%             -z_{S'} 
%             =
%             z_{S'}
%             - 
%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
%             .
%         \end{align*}
        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
        \begin{align*}
            \Theta_{|K}( h_z ) 
            &= 
            h_z
            - 
            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
            = 
            h_z
            - 
            2 z_{S'} \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle}
            %\\&
            = 
            h_z
            - 
            2 z_{S'}
            %\\&
            = 
            - h_{z}
            - 
            2 b_{z}
            .
        \end{align*}
        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
        We study the singular values of the matrix 
        \begin{align*}
            B 
            := 
            \begin{pmatrix}
            -1                 & 0
            \\ 
            -2 \|b_z\|/\|h_z\| & 1
            \end{pmatrix}
            =
            \begin{pmatrix}
            -1             & 0
            \\ 
            -2 \tan(\beta) & 1
            \end{pmatrix}
            .
        \end{align*}
        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
        Its square roots are the desired singular values of $B$:
        \begin{align*}
            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
            ,
            \\
            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
            .
        \end{align*}
        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
        whereas all its other singular values equal $1$.

@@

        \todo{TODO: Integrate the following paragraph and make it two-sided.}
        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz over some essentially disjoint closed partitions over their respective domains.
        It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
        Rademacher's theorem then shows that both have essentially bounded weak Jacobians almost everywhere.

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
% \usepackage{fullpage}
\input{header}

\usepackage{hyperref}         % For hypertext links
\usepackage{tikz-3dplot}      % 3d plots

@@

% DONE : MV : remove 'For example' 
We illustrate the subject of our discussion with the curl operator. 
% One example application concerns the curl operator. 
If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$. Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{2}(\Omega)}
    .
\end{align*}
The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
\color{blue}
Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
\color{black}
\\

@@

When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
as mappings between Lebesgue spaces. 
We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
\\
% DONE: cite Guzman and Salgado in a reasonable manner

@@

However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. % DONE: Theo : But -> However 
We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
In comparison to their exposition, our variants of the regularized potential operators are simplified:
we only study them over convex domains and use simpler (that is, constant) weight functions. 
The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
We consider the latter outcome to be of independent interest. 
% DONE \todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.

@@

% Future work % DONE: Theo : parts already mentioned ??? 
% Computable reliable estimates are important: 
% they quantify the fundamental stability properties of partial differential equations in vector analysis,
% such as the Hodge Laplace equation. 
There are several avenues for further research going from here. 
The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches. There are at least two points where the present techniques can be improved further. First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star. In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping. 
Better transformations or more careful estimates are likely possible, as are completely different approaches.  For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.

@@

This section is devoted to geometric operations that are crucially important for our main result. 
Suppose that we have a shellable simplicial complex. 
Every time we add a simplex according to the shelling sequence, 
we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
We will need a homeomorphism going from the new simplex onto its complement within the newly completed star.
This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
We are particularly interested in the norms of its Jacobian.
We inerpret this as a nonlinear reflection. It will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms.

In addition to that, this endeavor will produce another geometric tool 
that enables an additional estimate Poincar\'e--Friedrichs constants:
we construct a bi-Lipschitz deformation which maps the entire star 
into the complement of the newly completed star. 
Again, we give explicit estimates of the Jacobian.
\\

We begin with the following observation. 
Suppose that $T$ is any $n$-dimensional simplex with some proper subsimplex $F$.
We find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is on only one side of the hyperplane.

\begin{lemma}\label{lemma:oppositesubsimplex}
    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
    Let $F, F'$ be the two subsimplices of $T$ with respective vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
    Then $T$ lies on one side of the affine subspace
    \begin{gather*}
        A 
        := 
        v_0 
        + 
        \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} 
        +  
        \operatorname{lin}\{ v_{k+1} - v_n, \dots, v_{n-1} - v_n \}.
    \end{gather*}
    Moreover, $F = T \cap A$.
\end{lemma}
\begin{proof}
    Evidently, the linear spans 
    \begin{gather*}
        A_{0} := \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \},
        \qquad 
        A_{1} := \operatorname{lin}\{ v_{k+1} - v_n, \dots, v_{n-1} - v_n \}
    \end{gather*}
    intersect only at the origin, since otherwise the vertices of $T$ are not affinely independent. 
    So $A$ has dimension $n-1$. 
    Obviously, $F \subset A \cap T$. 
    Let us now suppose that $x \in A \cap T$.
    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
    \begin{align*}
        x &= 
        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
        \\&
        = 
        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
        + 
        \sum_{i=1  }^{k  } \lambda_{i} v_i 
        + 
        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
        + 
        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
        .
    \end{align*}
    We know that this is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive.
    But if $x \notin F$, then at least one of them must be negative,
    and thus their sum must be negative, which is a contradiction. 
    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are zero,
    which implies $x \in F$.
    The desired statement follows.         
\end{proof}

% \begin{figure}
% \tdplotsetmaincoords{60}{120}
% \centering
% \begin{tikzpicture}[tdplot_main_coords]
% \coordinate (A) at (0, 0, 0);
% \coordinate (B) at (2, 0, 0);
% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
% \coordinate (A) at (0, 0, 0);
% \coordinate (B) at (2, 0, 0);
% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
% \draw[thick] (A) -- (B) 
% \draw[] (B) -- (C) 
% \draw[] (C) -- (A) 
% \draw[] (A) -- (D);
% \draw[thick] (B) -- (D);
% \draw[] (C) -- (D);
% \node at (A) [below left] {$A(0,0,0)$};
% \node at (B) [below right] {$B(2,0,0)$};
% \node at (C) [above right] {$C(1,\sqrt{3},0)$};
% \node at (D) [above] {$D(1, \frac{1}{\sqrt{3}}, \sqrt{\frac{8}{3}})$};
% \end{tikzpicture} 
% \caption{test}
% \end{figure}

@@

% \begin{lemma}\label{lemma:stardivision}
%     Let $\calT$ be an $n$-dimensional simplicial complex
%     such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
%     Let $z_S$ be the barycenter of $S$ 
%     and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
%     If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
%     then $\vol(T^{\star}) = \vol(T) / n$.
% \end{lemma}
\begin{lemma}\label{lemma:stardivision}
    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$,
    let $z_S$ be the barycenter of $S$, 
    and let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ at $z_{S}$.
    Then $\vol(T') = \vol(T) / n$. 
\end{lemma}
\begin{proof}
    This is easy.
\end{proof}

We know construct the main result of this section, namely the desired bi-Lipschitz homeomorphism. 
It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
The construction is completed in several steps,
and the Lipschitz estimate reflects the shape regularity.

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
    Let $S \in \calT$ be a simplex of dimension $k < n$,
    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
    and let 
    \begin{align*}
        U := \overline{ |\patch_{\calT}(S)| \setminus T },
        \qquad 
        {\Gamma_1} := U \cap T,
        \qquad 
        {\Gamma_2} := \overline{ \partial T \setminus \partial U }.
    \end{align*}
    \begin{enumerate}
    \item 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi_{1} : T \rightarrow U
    \end{align*}
    which is the identity along ${\Gamma_1} = T \cap U$ and which satisfies the upper bounds 
    \begin{gather*}
        \| \Jacobian\Xi_{1} \|          \leq \Cfive{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi_{1}^{-1} \|     \leq \Csechs{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi_{1} \|      \leq \Cdetfive{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi_{1}^{-1} \| \leq \Cdetsechs{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
    \item 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi_{2} : T \rightarrow U
    \end{align*}
    which is the identity along $\partial U \setminus \partial T$ and which satisfies the upper bounds 
    \begin{gather*}
        \| \Jacobian\Xi_{2} \|          \leq \Csieb{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi_{2}^{-1} \|     \leq \Cacht{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi_{2} \|      \leq \Cdetsieb{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi_{2}^{-1} \| \leq \Cdetacht{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
    \end{enumerate}
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
        whereas ${\Gamma_1} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.

@@

        \item 
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ as follows.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}
        By construction, the mapping preserves volumes:
        \begin{align*}
            |\det( \Jacobian      \Theta_{|K} )|
            = 
            |\det( \Jacobian^{-1} \Theta_{|K} )|
            =
            1
            .
        \end{align*}
        We want to characterize the singular values of this transform. 
        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
        We can write
        \begin{align*}
            \Theta_{|K}(x) 
            = 
            x
            - 
            2 \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
            \hat z_{S'}
            .
        \end{align*}
        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_z$,
        and that it equals $-z_{S'}$ when $x = z_{S'}$.
%         and when $x = z_{S'}$, then 
%         \begin{align*}
%             -z_{S'} 
%             =
%             z_{S'}
%             - 
%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
%             .
%         \end{align*}
        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
        \begin{align*}
            \Theta_{|K}( h_z ) 
            &= 
            h_z
            - 
            2 \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle} z_{S'}
            = 
            h_z
            - 
            2 \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle} z_{S'}
            %\\&
            = 
            h_z
            - 
            2 z_{S'}
            %\\&
            = 
            - h_{z}
            - 
            2 b_{z}
            .
        \end{align*}
        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
        We study the singular values of the matrix 
        \begin{align*}
            B 
            := 
            \begin{pmatrix}
            -1                 & 0
            \\ 
            -2 \|b_z\|/\|h_z\| & 1
            \end{pmatrix}
            =
            \begin{pmatrix}
            -1             & 0
            \\ 
            -2 \tan(\beta) & 1
            \end{pmatrix}
            .
        \end{align*}
        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
        Its square roots are the desired singular values of $B$:
        \begin{align*}
            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
            ,
            \\
            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
            .
        \end{align*}
        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
        whereas all its other singular values equal $1$.

@@

        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
        It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
        Rademacher's theorem then shows that both have essentially bounded weak Jacobians.

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
        \todo{not enough}
